% Simple Overleaf LaTeX Template
\documentclass{article}

% Title and Author
\title{Comments}
\author{Tim Kircali}
\date{\\ \small Comments: Add your notes here}

\begin{document}

\maketitle

% Start writing your content below
\section{Comments Kurt Schmidheiny}
\begin{itemize}
    \item We should address the elephant in the room, the data privacy aspect, much more. 
    \item Either we could do that by having a separate treatment or by having more questions addressing it. 
    \item It is super relevant to know what the government is able to do with the data and \textit{whether they can trust the government to protect it.}
    \begin{itemize}
        \item So we might want to include a question which explicitly asks whether respondents think one could trust the government with the data. So far, we mainly ask whether the government can be trusted in general.
    \end{itemize}
    \item He mentioned that we should consider the explicit cost of facing the risk of making mistakes when filing. "You never know if you did it right"
    \item We have to include something more precise to understnad whether people can trust the government with handling the data. 
    \item The most important point he mentioned is that it is not clear enough which data comprehensive third party reporting covers. People could think about completely different sets of data when evaluating their effects. E.g. those treated in the filing treatment might have a different understanding of comprehensive third party reporting as those treated in the other treatments. 
    \begin{itemize}
        \item We were discussing whether bundling both policies into one, namely just calling it comprehensive third party reporting would be a problem. And I think it was not and would be an option. 
        \item So we could give them information (possibly using a video) on which data would exactly be involved in data
    \end{itemize}
    \item He was also not very convinced by this inequality aspect.
    \begin{itemize}
        \item I think it would be important to directly have a link to the appendix where we show to which findings in the literature we are referring to.
    \end{itemize}
    \item This showed again how precise we have to be in the paper + in seminars with which information is actually relevant for enforcement and for filing. 
\end{itemize}

\section{Comments Isabel Z. Martinez}



\section{Comments Felix Chopra}
\begin{itemize}
    \item We do not necessarily need the full info treatment!
    \item It would just be very important if we concentrated on policy question: How can we reach high support for information exchange through communication
    \item It is rather not important if we concentrate on channels. (self and society)
    \item Government fund use channel is important. What are peoples understanding on where this money should be spent. Should the government even raise more tax revenue? 
    \item He is not super convinced by the inequality treatment. Because he is not convinced by an inequality channel. 
    \item To publish: Super data or super survey. 
    \item I should consider using obfuscated follow up study for the petitions
    \item we do not have to incentivize
    \item open ended: thinks it would be super interesting
    \item survey provider: Prolific, 
    \item We should run: Attention checks, Captcha, Include an open question that is completely unrelated to see how quick people respond: zb lieblingsmonat, use audio+video because chatpgt add on is not able to listen to audio. 
look at the mission possible paper again: it shows that 
\end{itemize}


\section{Comments Dominika Langenmayr}
\begin{itemize}
    \item made a useful comment about the diffference of IEI and AEoI.
    \item suggests to elicit what people think who the tax evaders actually are.
\end{itemize}


\section{Comments Claus Kreiner}
\begin{itemize}
    \item international context would be super nice
    \item government questions important: should the government be able to tax that much
    
\end{itemize}

\section{Other comments}

\section{Julien Senn + Ernst Fehr}
\begin{itemize}
    \item Julien: Measure sentiments after treatments
    \item Ernst: Videos are propaganda
\end{itemize}

\end{document}
